\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass[journal]{IEEEtran}
\usepackage[a5paper, margin=10mm, onecolumn]{geometry}
%\usepackage{lmodern} % Ensure lmodern is loaded for pdflatex
\usepackage{tfrupee} % Include tfrupee package

\setlength{\headheight}{1cm} % Set the height of the header box
\setlength{\headsep}{0mm}     % Set the distance between the header box and the top of the text

\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
% \usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\usepackage{circuitikz}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{}
\author{EE24BTECH11053 - S A Aravind Eswar
}
% \maketitle
% \newpage
% \bigskip
{\let\newpage\relax\maketitle}

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\intextsep}{10pt} % Space between text and floats


\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\renewcommand{\thetable}{\theenumi}


\begin{enumerate}
    \item The probablity of a resistor being defective is 0.02. There are 50 such resistors in a circuit. The probability of two or more defective resistors in the circuit (round off to two decimal places) is \underline{\hspace{3cm}}.\hfill{[2019 - EE]}
    \item A 0.1 $\mu$F capacitor charged to 100 $V$ is discharged through  1 $k\Omega$ resistor. The time in $ms$ (round off to two decimal places) required for the voltage across the capacitor to drop to 1 $V$ is \underline{\hspace{3cm}}.\hfill{[2019 - EE]}
    \item The current $I$ flowing in the circuit shown below in amperes is \underline{\hspace{3cm}}.\hfill\\\strut\hfill{[2019 - EE]}\\
        \begin{center}
            \input{./figs/fig1.tex}
        \end{center}
    \item The volatage across and the current through a load are expressed as follows 
        \begin{align*}v(t) &= -170 \sin \brak{377t - \frac{\pi}{6}} V\\i(t) &= 8\cos\brak{377t+\frac{\pi}{6}} A\end{align*}
        The average power in watts (round off to one decimal place) consumed by the load is \underline{\hspace{3cm}}.\hfill{[2019 - EE]}
    \item The magnetic circuit shown below has uniform cross-section area and air gap of 0.2$cm$. The mean path length of the core is 40$cm$. Assume that leakage and fringing fluxes are negligible. When the core relative permeability is assumed to be infinite, the magnetic flux density computed in the air gap is 1 tesla. With the same Ampere-turns, if the core relative permeability is assumed to be 1000 (linear), the flux density in tesla (round off the three decimal places) calulated in the air gap is \underline{\hspace{3cm}}. \hfill{[2019- EE]}
        \begin{center}
            \input{./figs/fig2.tex}
        \end{center}
\item A single-phase transformer of rating 25$kVA$, supplies a 12$kW$ load at power factor 06 lagging. The additional load at unirt power factor in $kW$(round off to two decimal places) that may be added before this transformer exceeds it's rated $kVA$ is \underline{\hspace{3cm}}. \hfill{[2019 - EE]}
\item A 220$V$ CD shunt motor takes 3$A$ at no-load. It draws 25$A$ when running at full-load at 1500 rpm. The armature and shunt resistances are 0.5 $\Omega$ and 220 $\Omega$, respectively. The no-load speed in rpm (round off to two decimal places) is \underline{\hspace{3cm}}. \hfill{[2019 - EE]}
\item A delta-connected, 3.7 $kW$, 400 $V$(line), three-phase, 4-pole, 50-$Hz$ squirrel-cage induction motor has the following equivalent circuit parameters per phase referred to the stator: $R_1 - 5.39 \Omega, R_2 = 5.72 \Omega, X_1 = X_2 = 8.22 \Omega$. Neglet shunt branch in the equivalent circuit. The starting line current in amperes (round off the two decimal places) when it is connected to a 100 $V$ (line), 10 $Hz$, three-phase AC source is \underline{\hspace{3cm}}. \hfill{[2019 - EE]}

\item A 220 $V$ (line), three-phase, Y-connected, synchronous motor has a synchorous impedance of $(0.25 + j2.5)\Omega$/phase. The motor draws the rated current of 10 $A$ at 0.8 $pf$ leading. The rms value of line-to-line internal voltage in volts (round off to two decimal places) is \underline{\hspace{3cm}}. \hfill{[2019 - EE]}
\item A three-phase 50 $Hz$, 400 $kV$ transmission line is 300 $km$ long. The line inductance is 1 $mH/km$ per phase, and the capacitance is 0.01 $\mu F/km$ per phase. The line is under open circuit condition at the receiving end and energized with 400 $kV$ at the sending end, the receiving end line voltage in $kV$ (round off to two decimal places) will be \underline{\hspace{3cm}}. \hfill{[2019 - EE]}
\item A 30 $kV$, 50 $Hz$, 50 $MVA$ generator has the positive, negative, and zero sequence reactances of 0.25 $pu$, 0.15 $pu$, and 0.05 $pu$, respectively. The neutral of the generator is grounded with a reactance so that the fault current for a bolted LG fault and that of a bolted three-phase fault at the generator terminal are equal. The value of grounding reactance in ohms (round off to one decimal place) is \underline{\hspace{3cm}}. \hfill{[2019 - EE]}
\item In the single machine infinite bus system shown below, the generator is delivering the real power of 0.8 $pu$ at 0.8 power factor lagging to the infinite bus. The power angle of the generator in degrees (round off to one decimal place) is \underline{\hspace{3cm}}. \hfill{[2019 - EE]}
    \begin{center}
        \input{./figs/fig3.tex}
    \end{center}
    \item In a 132 $kV$ system, the series inductance up to the point of circuirbreaker locationis 50 mH. The shunt capasitance at the circuit breaker terminal is 0.05 $\mu F$. The critical value of resistance in ohm required to be connected across the circuit breaker contacts which will give no transient oscillation is. \underline{\hspace{3cm}}.\hfill{[2019 - EE]}
\end{enumerate}

\end{document}  

